Supplementary Figures relative to dimensionality reduction

### 2020-05-07 supplementary_figures/supp3_normalization.Rmd
added missing supp figures

```{r, fig.width=7.5, fig.height=6}
res <- readRDS("../data/results_norm.rds")
res <- res$elapsed$stepwise$normalization
ag <- aggregate(res[,"elapsed",drop=FALSE], by=res[,c("dataset","norm")], FUN=mean)
cols <- pipeComp::getQualitativePalette(9)
names(cols) <- levels(ag$dataset)
ggplot(ag, aes(norm, elapsed)) + geom_boxplot() + geom_point(aes(colour=dataset)) + 
  coord_flip() + scale_colour_manual(values=cols) + ylab("") + xlab("Time (s)")
```

>>>>

```{r, fig.width=7.5, fig.height=6}
res <- readRDS("../data/results_norm.rds")
res <- res$elapsed$stepwise$normalization
ag <- aggregate(res[,"elapsed",drop=FALSE], by=res[,c("dataset","norm")], FUN=mean)
cols <- pipeComp::getQualitativePalette(9)
names(cols) <- levels(ag$dataset)
ggplot(ag, aes(norm, elapsed)) + geom_boxplot() + geom_point(aes(colour=dataset)) + 
  coord_flip() + scale_colour_manual(values=cols) + xlab("") + ylab("Time (s)")
```

### 2020-05-07 supplementary_figures/supp5_dr.Rmd
added missing supp figures

p2 <- renameHrows(
  evalHeatmap( res, what=c("MI","min_pr"), agg.by=c("norm","dr"), reorder_rows=TRUE, anno_legend=FALSE,
               title=c("MI","Minimum precision")) + 
  evalHeatmap(res, what=c("ARI"), agg.by=c("norm","dr"), filterExpr=n_clus==true.nbClusts, 
              anno_legend=FALSE, title="ARI at true k"),
  function(x) gsub("norm\\.","",x)
)
p2 <- grid.grabExpr(draw(p2))

@@

### Supplementary Figure `r getFigNb()`
Silhouette width (**A**) per subpopulation and clustering accuracy (**B**) according to various normalization and dimension reductions.
**Evaluation of common dimensionality reduction methods. A:** Minimum (left) and average (right) silhouette width per subpopulation resulting from combinations of normalization and dimension reductions. **B:** Clustering accuracy, measured by mutual information (MI), minimum subpopulation precision, and adjusted Rand index (ARI) at the true number of clusters.

>>>>

p2 <- renameHrows(
  evalHeatmap( res, step="clustering", what=c("MI","min_pr"), agg.by=c("norm","dr"), 
               reorder_rows=TRUE, anno_legend=FALSE, title=c("MI","Minimum precision")) + 
  evalHeatmap(res, step="clustering", what=c("ARI"), agg.by=c("norm","dr"), 
              filterExpr=n_clus==true.nbClusts, anno_legend=FALSE, title="ARI at true k"),
  function(x) gsub("norm\\.","",x)
)
p2 <- grid.grabExpr(draw(p2))

@@

### Supplementary Figure `r getFigNb()`
**Evaluation of common dimensionality reduction methods. A:** Minimum (left) and average (right) silhouette width per subpopulation resulting from combinations of normalization and dimension reductions. **B:** Clustering accuracy, measured by mutual information (MI), minimum subpopulation precision, and adjusted Rand index (ARI) at the true number of clusters.
